\colophontitle{Amige, Don't Read This Colophon!}
\begin{colophon}
... what are you doing. I told you explicitly NOT to! Now I need to actually come up with text for a colophon! Do you know how much copy you need to write for a colophon? Like, A FULL PAGE! ZOMG, THE HORROR!!\footnotemark

Uh... right... so... moving straight past that:

\emph{Why hello there!} I sure hope you are finding yourself to be having an excellent day, today. Certainly a good one for hacking your console to teach it new tricks!
\IfLanguageName{english}{Speaking of, I would like to point out that I am not actually the original author of this doc - I just translated it! @jayp76 started this, I'm just trying to help out!}{}
\IfLanguageName{german}{Don't worry, this is indeed the German version of this PDF. But I'm writing in English to highlight that I'm NOT the original author of this document - you should head on over to jayp76's github for that, yo!}{}

And thanks to the magicks of github and how that fosters collaboration, that's exactly what you too can do! I saw this, forked it, and sent pull requests. It's github. It's awesome. You can do it too!

So... since I did not have the source document, and it was very likely one of those Cloud Word Processors anyway, I translated this doc into LaTeX first, then over to English. LaTeX because it's a very simple file format and it produces really nice PDFs - or printable output in general - so it also works much better under version control, like with Git. This means the PDFs have clickable hyperlinks and generally enjoy really solid formatting - whenever I'm not actively trying to break it, like here.

\IfLanguageName{german}{As for the contents of this document, that's all jayp76 - I wouldn't want to wish my horrible German on ye. Alemannisch I can do tho... maybe another translation for another rainy weekend. I have not done a proper proof-reading pass, but I also didn't see any glaring typos.}{}

Also, I have not actually tried all the things in this doc first-hand. I did try my best to keep the English consistent throughout, but it's totally possible some German slipped past - I mean, English slipped into the German version, right? So, if you find mistakes, however large: you get to keep both pieces. Pitch in and send a pull request with a fix. It's just LaTeX, it's not that hard.

You \emph{can DO IT}!

This was @EffinMaggie, and you go have a good day there now. Go apply what you read here into getting down with some new games on your Retron!

And stop reading colophons. They've not been hip since the 16th century. Like, you're gonna make FETCH happen before colophons are back in style, and after the time we've all had, YOU most DEFINITELY deserve yourself some FRESH STYLES! Have fun!

\end{colophon}

\footnotetext{... no, I don't have a thing going on about breaking style in otherwise meticulously crafted forms of publishing. That is a very specific thought, why would you think that? Have you been spying on my Twitter or Twitch? 'cause you shouldn't do that. At least not the Twitter - that's a terrible place. Made of terrible people. Like me. Also I broke a LaTeX package in the making of this joke, and you are probably never going to read this, unless you check the source. If you do: Good on you, mate! Well done! Curiosity might kill cats, but if you're reading English, you likely aren't one, so you're good, and learning! Huzzah!}

